Results Text

### 2024-03-12 Fish Data Analysis/NN_Accel_Heading.qmd
Commit before writing, final graphs

# fish_comp_data_switch_fish <- fish_comp_data %>% mutate(Fish3 = Fish1,
#                                               Fish3_X = Fish1_X,
#                                               Fish3_Y = Fish1_Y,
#                                               Fish3_Z = Fish1_Z,
#                                               Fish3_Speed = Fish1_Speed,
#                                               Fish3_Accel = Fish1_Accel,
#                                               Fish3_Yaw_Heading = Fish1_Yaw_Heading,
#                                               Fish3_Yaw_Heading_PS = Fish1_Yaw_Heading_PS
#                                               ) %>%
#                                        mutate(Fish1 = Fish2,
#                                               Fish1_X = Fish2_X,
#                                               Fish1_Y = Fish2_Y,
#                                               Fish1_Z = Fish2_Z,
#                                               Fish1_Speed = Fish2_Speed,
#                                               Fish1_Accel = Fish2_Accel,
#                                               Fish1_Yaw_Heading = Fish2_Yaw_Heading,
#                                               Fish1_Yaw_Heading_PS = Fish2_Yaw_Heading_PS) %>%
#                                        mutate(Fish2 = Fish3,
#                                               Fish2_X = Fish3_X,
#                                               Fish2_Y = Fish3_Y,
#                                               Fish2_Z = Fish3_Z,
#                                               Fish2_Speed = Fish3_Speed,
#                                               Fish2_Accel = Fish3_Accel,
#                                               Fish2_Yaw_Heading = Fish3_Yaw_Heading,
#                                               Fish2_Yaw_Heading_PS = Fish3_Yaw_Heading_PS) %>%
#                                        #Switch around angle when we switch focal fish
#                                        mutate(Angle = ifelse(Angle >= 0, Angle - pi, Angle + pi),
#                                               Relative_X = -1*Relative_X) %>%
#                                        select(-c(Fish3,Fish3_X,Fish3_Y,Fish3_Z,Fish3_Speed,Fish3_Accel,Fish3_Yaw_Heading,Fish3_Yaw_Heading_PS))
# 
# fish_comp_data_combo <- bind_rows(fish_comp_data, fish_comp_data_switch_fish)

min_dist <- 0
max_dist <- 3

fish_data_nn <- fish_comp_data %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(#nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = nth_min(Distance, 1),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    #filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    #filter(row_n == 1) %>%
                                    ungroup() %>%
                                    filter(Distance >= min_dist & Distance <= max_dist)

fish_data_nn_normal <- fish_data_nn %>% group_by(Flow_Ablation_Darkness) %>%
                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
                                        ungroup()

@@

@@

#Raw data
ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
       aes(x = Angle, y = rad2deg(Fish2_Yaw_Heading_PS), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(alpha = 0.1)+
  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
  geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
  theme_classic() +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line()+
  geom_line(aes(y = rad2deg(predict(manual_model,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
  theme_classic() +
  ylim(-50,50) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle speed (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")+
  ggtitle(paste0("Nearest Neighbor From ",min_dist," to ",max_dist))

>>>>

single_fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D_Single.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "S", "Single", "???")) %>%
                           mutate(Darkness = ifelse(Darkness == "S", "Single", "???")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("Single"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Single"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"))

single_fish_comp_data <- na.omit(single_fish_comp_data)

all_fish_comp <- rbind(fish_comp_data,single_fish_comp_data)

min_dist <- 4
max_dist <- 10

fish_data_nn <- all_fish_comp %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(#nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = nth_min(Distance, 1),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    #filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    #filter(row_n == 1) %>%
                                    ungroup() %>%
                                    filter(Distance >= min_dist & Distance <= max_dist)

fish_data_nn_normal <- fish_data_nn %>% group_by(Flow_Ablation_Darkness) %>%
                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T)) %>%
                                        ungroup()

@@

Load in Single Fish

@@

#Raw data
ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
       aes(x = Angle, y = rad2deg(Fish2_Yaw_Heading_PS), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(alpha = 0.1)+
  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
  geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
  theme_classic() +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")

#Means graph
ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line()+
  geom_line(aes(y = rad2deg(predict(manual_model,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
  theme_classic() +
  #ylim(-50,50) +
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle speed (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")+
  ggtitle(paste0("Nearest Neighbor From ",min_dist," to ",max_dist))

### 2024-03-12 Fish Data Analysis/Paper_Figures.qmd
Commit before writing, final graphs

```{r}
fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"))

@@

min_dist <- 0
max_dist <- 3

fish_data_nn_normal <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
                                        group_by(Flow_Ablation_Darkness) %>%
                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
                                        ungroup()

nn_heading_sum <- fish_data_nn_normal %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()
```

@@

heading_PS_model_still <- lm(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness, 
                   data = fish_data_nn_normal %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_still)

heading_PS_graph <- ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_still,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins)))), size = 1)+
  theme_classic() +
  ylim(-50,50) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")

heading_PS_graph

ggsave("Paper Figures/Heading_PS_Graph.jpg", heading_PS_graph, width = 7, height = 7)

>>>>

```{r}
fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>%

                           # ### Used to remove every third point to reduce autocorrelation
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
                           group_by(Comp_ID) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup()

@@

close_min_dist <- 0
close_max_dist <- 3

far_min_dist <- 3
far_max_dist <- 100

fish_data_nn_normal_close <- fish_comp_data %>% filter(Distance >= close_min_dist & Distance <= close_max_dist) %>%
                                        group_by(Flow_Ablation_Darkness) %>%
                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
                                        ungroup()

nn_heading_sum_close <- fish_data_nn_normal_close %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

fish_data_nn_normal_far <- fish_comp_data %>% filter(Distance >= far_min_dist & Distance <= far_max_dist) %>%
                                        group_by(Flow_Ablation_Darkness) %>%
                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
                                        ungroup()

nn_heading_sum_far <- fish_data_nn_normal_far %>% mutate(angle_bins = round_any(Angle,pi/6)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()
```

@@

heading_PS_model_close <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_close)

heading_PS_model_far <- lmer(Fish1_Yaw_Heading_PS ~ 0 + sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
Anova(heading_PS_model_far)

heading_PS_graph_close <- ggplot(nn_heading_sum_close %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_close,
                    newdata = nn_heading_sum_close %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
                    re.form = NA))), size = 1)+
  theme_classic() +
  ylim(-75,75) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum_close$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum_close$angle_bins))) +
  labs(color = "Sensory Conditions")

heading_PS_graph_far <- ggplot(nn_heading_sum_far %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(aes(y = rad2deg(predict(heading_PS_model_far,
                    newdata = nn_heading_sum_far %>% filter(Flow == "Still Water") %>% mutate(Angle = angle_bins),
                    re.form = NA))), size = 1)+
  theme_classic() +
  ylim(-75,75) +
  xlab("Direction of Neighbour (Degrees)") +
  ylab("Focal Fish Turning Angle Speed (Degrees/Sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum_far$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum_far$angle_bins))) +
  labs(color = "Sensory Conditions")

heading_PS_graph_close
heading_PS_graph_far

heading_PS_mega_plot <- ggarrange(heading_PS_graph_close, heading_PS_graph_far, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1, common.legend = TRUE, legend="right")

heading_PS_mega_plot

ggsave("Paper Figures/heading_PS_mega_plot.png", heading_PS_mega_plot, width = 14, height = 7)

### 2024-03-12 Fish Data Analysis/Results_Text.qmd
Commit before writing, final graphs

ggplot(school_data, aes(x = 1, y = NND, color = Flow_Ablation_Darkness))+
  geom_point()+
  facet_wrap(~Date_Trial)
```

@@

glmm_school_stats_table <- tibble(Stat = c(rep("NND",6),rep("Polarization",6),rep("Speed",6),rep("Groups",6)),
       Flow_or_Still = rep(c(rep("Still",3) , rep("Flow",3)), 4),
       Condition = rep(c("Ablation","Darkness","Ablation:Darkness"), 8),
       DF = rep(c(rep(length(nnd_lmer_still@resp$y)-3,3),
                  rep(length(nnd_lmer_flow@resp$y)-3,3)),times = 4),
       Chisq = round(c(nnd_s_aov_me$Chisq[1:3],nnd_f_aov_me$Chisq[1:3],
                 polar_s_aov_me$Chisq[1:3],polar_f_aov_me$Chisq[1:3],
                 speed_s_aov_me$Chisq[1:3],speed_f_aov_me$Chisq[1:3],
                 groups_s_aov_me$Chisq[1:3],groups_f_aov_me$Chisq[1:3]),2),

@@

@@

>>>>

                            # ### Used to remove every third point to reduce autocorrelation
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_"),
                                  Comp_ID = paste(Year,Month,Day,Trial,Fish1,Fish2, sep = "_")) %>%
                           group_by(Comp_ID) %>%
                           filter(row_number() %% 3 == 1) %>%
                           ungroup()
```

@@

glmm_school_stats_table <- tibble(Stat = c(rep("NND",6),rep("Polarization",6),rep("Speed",6),rep("Groups",6)),
       Flow_or_Still = rep(c(rep("Still",3) , rep("Flow",3)), 4),
       Condition = rep(c("Ablation","Darkness","Ablation x Darkness"), 8),
       DF = rep(c(rep(length(nnd_lmer_still@resp$y)-3,3),
                  rep(length(nnd_lmer_flow@resp$y)-3,3)),times = 4),
       Chisq = round(c(nnd_s_aov_me$Chisq[1:3],nnd_f_aov_me$Chisq[1:3],
                 polar_s_aov_me$Chisq[1:3],polar_f_aov_me$Chisq[1:3],
                 speed_s_aov_me$Chisq[1:3],speed_f_aov_me$Chisq[1:3],
                 groups_s_aov_me$Chisq[1:3],groups_f_aov_me$Chisq[1:3]),2),

@@

fish_comp_data <- read.csv("Data/Fish_Comp_Values_3D.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           separate(Fish, c("Fish1", "Fish2"),sep="x") %>% 
                           mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"),
                                  Date = paste(Year,Month,Day,Trial, sep = "_"),
                                  Fish_ID = paste(Year,Month,Day,Trial,Fish1, sep = "_")) %>%

fish_comp_data <- na.omit(fish_comp_data)

close_min_dist <- 0
close_max_dist <- 3

far_min_dist <- 3
far_max_dist <- 10

fish_data_nn_normal_close <- fish_comp_data %>% filter(Distance >= close_min_dist & Distance <= close_max_dist) %>%
                                        group_by(Flow_Ablation_Darkness) %>%
                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
                                        ungroup()

fish_data_nn_normal_far <- fish_comp_data %>% filter(Distance >= far_min_dist & Distance <= far_max_dist) %>%
                                        group_by(Flow_Ablation_Darkness) %>%
                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS)) %>%
                                        ungroup()

@@

heading_PS_model_close <- lmer(0 + Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date), 
                   data = fish_data_nn_normal_close %>% filter(Flow == "Still Water")) 
aov_heading_PS_model_close <- Anova(heading_PS_model_close)

test(emmeans(heading_PS_model_close, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))

heading_PS_model_far <- lmer(0 + Fish1_Yaw_Heading_PS ~ sin(Angle) + sin(Angle):Ablation + sin(Angle):Darkness + sin(Angle):Ablation:Darkness + (1|Date) , 
                   data = fish_data_nn_normal_far %>% filter(Flow == "Still Water")) 
aov_heading_PS_model_far <- Anova(heading_PS_model_far)

test(emmeans(heading_PS_model_far, pairwise ~Ablation*Darkness | Angle, at = list(Angle = c(pi/2))))

turning_school_stats_table <- tibble(
       Near_or_Far = rep(c(rep("Near",4) , rep("Far",4)), 1),
       Condition = rep(c("Angle","Angle x Ablation","Angle x Darkness","Angle x Ablation x Darkness"), 2),
       DF = c(rep(length(heading_PS_model_close@resp$y)-4,4),
                  rep(length(heading_PS_model_far@resp$y)-4,4)),
       Chisq = round(c(aov_heading_PS_model_close$Chisq[1:4],aov_heading_PS_model_far$Chisq[1:4]),3),
       P_Val = round(c(aov_heading_PS_model_close$`Pr(>Chisq)`[1:4],aov_heading_PS_model_far$`Pr(>Chisq)`[1:4]),3),
       Is_Sig = P_Val < 0.05)

turning_school_stats_table

tab_df(turning_school_stats_table, file="turning_stats.doc")
